\sysfull

### 2017-11-17 paper/evaluation.tex
eval: todo about 0 instead of X

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/ramPagsSizes}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\textbf{\sys normalized runtime for various page sizes, \{32, 64, $\ldots$,1024\}\,bytes, per application (top) and respective page faults (bottom)}; X: no page faults.}
	\label{fig:page_size}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/ramPagsSizes}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\textbf{\sys normalized runtime for various page sizes, \{32, 64, $\ldots$,1024\}\,bytes, per application (top) and respective page faults (bottom)}; X: no page faults. \todo{change X to 0, remove the definition of X from caption}{Amjad}}
	\label{fig:page_size}
\end{figure}
